Characterization of gaps in directly bonded Si compound optics

### 2014-05-01 AO_bondedSi.tex
Add a huge table- Experiment Log for all experiments so far
corrections to Tables, inclusion of details on VG07 and VG08

\begin{table}[h!]
\caption{UTexas Si bonding experiments \label{tabbondexper}}
\begin{center}
    \begin{tabular}{ c c c c c c}
    \hline
    Name & Diameter & Thickness & Pattern Type & Pattern Depth & Notes \\ 
    -  & mm & mm & - & nm & - \\ 
        \hline
    VG01  & 100  &$1$ $\times$ 2 & None  & - &  \\
    VG02   & 100 & $3.3$ $\times$ 2 &  None  & - &  \\
    VG03   & 100 & $3.3$ $\times$ 2 &  Hole \&Petal & 4000$\pm$200 & See Fig. \ref{figVG03pattern}\\    
    VG04   & 100 & $1$ $\times$ 2 &  Patchwork Islands & 15 & \\
    VG09   & 75 & $1$ $\times$ 2 & mesh C & 49 $\pm$6 & \\
    VG15   & 100 & $0.8$ $\times$ 2 &  mesh C, M, F  &14 $\pm$2 & \\
    VS20   & 100 & $0.8$ $\times$ 2 &  mesh C, M, F & 95 $\pm$5 & See Fig. \ref{figVS20pattern}\\
    \hline
    \end{tabular}
\end{center}
\end{table}

\begin{table}[h!]
\caption{Patterned gap properties \label{tabPatternFills}}
\begin{center}
    \begin{tabular}{ c c c c }
    \hline
    Pattern name & fill factor & minimum feature size & bulk description \\ 
    - & \% & $\mu$m & '- \\ 
    Hole & 100 & - & 25 mm diameter hole \\     
    Petal & $\sim1$ & $\sim$2000 & long petal lines, Fig. \ref{figVG03pattern} \\         
    Mesh F & 50 & 40 &  100 $\mu$ square holes, Fig. \ref{figVS20pattern}\\ 
    Mesh M & 50 & 200 &  500 $\mu$ square holes\\ 
    Mesh C & 50 & 620 &  1500 $\mu$ square holes\\     
        \hline
    \end{tabular}
\end{center}
\end{table}

@@

\begin{table}[h!]
\caption{Summary of Cary 5000 Measurement parameters \label{tab:Cary5000pars}}
\begin{center}
\begin{tabular}{ c c }
\hline
        Parameter (Units) & Value \\ 
\hline
        Spectral sampling interval (nm) & 2.0 \\
        Spectral resolution (nm) & 5 \\
        Time per sample (s) & 0.1 \\
        Available measurement range (nm) & 175-3300 \\
        Typical measurement range (nm) & 1000-2500 \\
	Single mode RMS  (\%) & 0.02 \\
	Double mode RMS  (\%) & 0.002 \\
	Typical Single mode mean drift (\%) & 0.20 \\
	Typical Double mode mean drift (\%) & 0.02 \\
	No beam dark signal (\%) & 0.03 \\
 	Beam size (mm $\times$ mm) & $2 \times 8$ \\
	Wavelengths of instrumental artifacts (nm) & - \\
        		 & 1200 \\
		 & 1350 \\
		 & 1360-1450\\
		 & 1850 \\
		 & 1800-1950 \\
		 & 2000 \\
        Vendor-reported linearity range (dB) & $>40$ \\
        Directly measured linearity range (dB) & $>24$ \\
    \hline
    \end{tabular}
\end{center}
\end{table}

@@

>>>>

\begin{table}[h!]
\caption{UTexas Si bonding experiments \label{tabbondexper}}
\begin{center}
    \begin{tabular}{ c c c c c c}
    \hline
    Name & Diameter & Thickness & Pattern Type & Pattern Depth & Notes \\ 
    -  & mm & mm & - & nm & - \\ 
        \hline
    HA1     & 75   & $10$ $\times$ 2& None & - & \\
    VG01   & 100 &$1$ $\times$ 2 & None  & - &  \\
    VG02   & 100 & $3.3$ $\times$ 2 &  None  & - &  \\
    VG03   & 100 & $3.3$ $\times$ 2 &  Hole \&Petal & 4000$\pm$200 & See Fig. \ref{figVG03pattern}\\    
    VG04   & 100 & $1$ $\times$ 2 &  Patchwork Islands & 15$\pm7$ & \\
    VG07   & 100 & $1$ $\times$ 2 &  mesh C, M, F & 12$\pm7$ & \\ %see email from Victor on 5/16/13
    VG08   & 100 & $1$ $\times$ 2 &  mesh C, M, F & 12$\pm7$ & \\ 
    VG09   & 75   & $1$ $\times$ 2 & mesh C & 49 $\pm$6 & \\
    VG15   & 100 & $0.8$ $\times$ 2 &  mesh C, M, F  &14 $\pm$2 & \\
    VS20   & 100 & $0.8$ $\times$ 2 &  mesh C, M, F & 95 $\pm$5 & See Fig. \ref{figVS20pattern}\\
    \hline
    \end{tabular}
\end{center}
\end{table}

\begin{table}[h!]
\caption{Patterned gap properties \label{tabPatternFills}}
\begin{center}
    \begin{tabular}{ c c c c }
    \hline
    Pattern name & fill factor & minimum feature size & bulk description \\ 
    - & \% & $\mu$m & - \\ 
    \hline
    Hole & 100 & - & 25 mm diameter hole \\     
    Petal & $\sim1$ & $\sim$2000 & long petal lines, Fig. \ref{figVG03pattern} \\         
    Mesh F & 50 & 40 &  100 $\mu$ square holes, Fig. \ref{figVS20pattern}\\ 
    Mesh M & 50 & 200 &  500 $\mu$ square holes\\ 
    Mesh C & 50 & 620 &  1500 $\mu$ square holes\\     
        \hline
    \end{tabular}
\end{center}
\end{table}

@@

\begin{table}[h!]
\caption{Summary of Cary 5000 Measurement parameters \label{tab:Cary5000pars}}
\begin{center}
\begin{tabular}{ c c }
\hline
        Parameter (Units) & Value \\ 
\hline
        Spectral sampling interval (nm) & 2.0$-$10.0 \\
        Spectral resolution (nm) & 5 \\
        Time per sample (s) & 0.1 \\
        Available measurement range (nm) & 175-3300 \\
        Typical measurement range (nm) & 1000-2500 \\
	Single mode RMS  (\%) & 0.02 \\
	Double mode RMS  (\%) & 0.002 \\
	Typical Single mode mean drift (\%) & 0.20 \\
	Typical Double mode mean drift (\%) & 0.02 \\
	No beam dark signal (\%) & 0.03 \\
 	Beam size (mm $\times$ mm) & $2 \times 8$ \\
	Wavelengths of instrumental artifacts (nm) & - \\
        		 & 1200 \\
		 & 1350 \\
		 & 1360-1450\\
		 & 1850 \\
		 & 1800-1950 \\
		 & 2000 \\
        Vendor-reported linearity range (dB) & $>40$ \\
        Directly measured linearity range (dB) & $>24$ \\
    \hline
    \end{tabular}
\end{center}
\end{table}

@@

% Table of experiments
\begin{table}[h!]
\caption{Cary5000 Experiment Log \label{tabExperiments}}
\begin{center}
    \begin{tabular}{c c c c c c c}
    \hline
	Date &  Mode  & $\Delta \lambda$ & SBW & Sampling & \# of spectra & Sample IDs \\
	\emph{mm/dd/yyyy} &  -  & nm & nm & nm & - \\
%     \hline		
%	02/04/2013 & ? & ? 				& 5.0 & 10.0 &  16 &   -  \\
%     \hline		
%	02/06/2013 & ? & ? 				& 5.0 & 10.0 &  16 &   -  \\	     
     \hline		
     	02/18/2013 & Single & 1000$-$2500 & 5.0 & 10.0 &  16 &   -  \\
     	                   &            &                       &       &         &    4 &  Baseline\\	
     	                   &            &                       &       &         &    1 &  VG01\\
	                   &            &                       &       &         &    4 &  VG02\\	                   
	                   &            &                       &       &         &    2 &  VG03\\	                   
	                   &            &                       &       &         &    2 &  VG04\\
	                   &            &                       &       &         &    2 &  VG05\\	                   
	                   &            &                       &       &         &    2 &  VG06\\
    \hline
%	05/02/2013 & Single & 1000$-$2500 & 5.0 & 5.0  &  30 &   -  \\
%     	                   &            &                       &       &         &    12 &  Baseline\\	
%     	                   &            &                       &       &         &    18 &  Other\\
%    \hline
	05/03/2013 & Single & 1000$-$2500 & 5.0 & 5.0  &  28 &   -  \\
     	                   &            &                       &       &         &    8 &  Baseline\\	
     	                   &            &                       &       &         &    1 &  VG05\\ %Consider replacing VG05 with "DSP reference sample"  or something
     	                   &            &                       &       &         &    6 &  VG03\\
     	                   &            &                       &       &         &    13 &  Other\\ %These had to do with beam size experiments
    \hline
	06/07/2013 & Mix & 1000$-$2500 & 5.0 & 5.0  &  43 &   -  \\
	                   &            &                       &       &         &    11 &  Baseline\\	                   
	                   &            &                       &       &         &    9 &  VG05\\	                   
	                   &            &                       &       &         &    7 &  VG07\\
	                   &            &                       &       &         &    6 &  VG08\\
	                   &            &                       &       &         &    4 &  HA1\\
	                   &            &                       &       &         &    6 &  other\\ % These are mostly just baselines without automatic division
    \hline
	08/02/2013 & Single & 1000$-$2500 & 5.0 & 2.0  &  17 &   -  \\	
	                   &            &                       &       &         &    3 &  Baseline\\
	                   &            &                       &       &         &    4 &  VG05\\	                   
	                   &            &                       &       &         &    2 &  VG15\\
	                   &            &                       &       &         &    2 &  VS20\\
	                   &            &                       &       &         &    6 &  VG09\\
    \hline
    	09/11/2013 & Double & 1000$-$2500 & 5.0 & 2.0  &  20 &   -  \\	                   
	                   &            &                       &       &         &    1 &  Baseline\\
	                   &            &                       &       &         &    14 &  VS21\\	                   
	                   &            &                       &       &         &    5 &  Blank\\ %This is really the same as a baseline
    \hline
    	09/16/2013 & Double & 1000$-$2500 & 5.0 & 2.0  &  21 &   -  \\
	                   &            &                       &       &         &    2 &  Baseline\\
	                   &            &                       &       &         &    7 &  VG07\\	                   
	                   &            &                       &       &         &    4 &  VG05\\	
	                   &            &                       &       &         &    4 &  VG12\\
	                   &            &                       &       &         &    2 &  VG15\\	                   
	                   &            &                       &       &         &    2 &  VG08\\
    \hline
    \end{tabular}
\end{center}
\end{table}
